Knowledge discovery in networked systems

### 2015-08-20 paper.tex
Update the technical report and update the new database file

\begin{itemize}
\item Use SAF to analyze Openstack logs. All related files can be found under
  ``declarative-log-analytics/codebase/case_study/novaboot''.
  \begin{itemize}
  \item Identify the normal execution logs to explore: osloganal/data/logs/new\_testbed24/novadelete/delete-0.log
  \item Convert the log in JSON into an SQLite3 database. (done)
  \item Convert the log in JSON into an event sqlite3 database required by \saf{}.
    \begin{itemize}
    \item The schema of the database should satisfy the format of the event in
      \saf{}.

@@

>>>>

\begin{itemize}
\item Use SAF to analyze Openstack logs. All related files can be found under
  ``declarative-log-analytics/codebase/case\_study/novaboot''.
  \begin{itemize}
  \item Identify the normal execution logs to explore: osloganal/data/logs/new\_testbed24/novadelete/delete-0.log
  \item Convert the log in JSON into an SQLite3 database. (done)
  \item Convert the log in JSON into an event sqlite3 database required by \saf{}.
    \begin{itemize}
    \item The schema of the database should satisfy the format of the event in
      \saf{}.

@@

\section{Code review comments}
\label{sec:codereview}

\begin{itemize}
\item Code logic: 
  \begin{enumerate}
  \item Create the event database from the database file (line 175).
  \item Create the global symbol table
  \item Parse the given model
    \begin{enumerate}
    \item parse header
    \item parse behavior
    \item parse model 
    \item (What's the difference between model and behavior?A: Model = combination of behaviors)
    \end{enumerate}
  \item Apply the parsed model over the data to get instances.
    \begin{enumerate}
    \item Create StateManager
    \item Create datahandle
    \item Create ModelProcessor
      \begin{enumerate}
      \item StateProcessor
      \item BehaviorConstraintProcessor
      \item LTLOpsProcessor
      \item ITLOpsProcessor
      \item LogicalOpsProcessor
      \end{enumerate}
    \item Apply models to the event database to fetch satisfying data (line 287)
    \end{enumerate}
  \end{enumerate}
\item Error: In behaviorinstance.py: comments for function definitions
  ``set\_dependee'' and ``get\_dependee''. Instead of ``the pointer to the
  behavior object'', should be ``the pointer to the dependent instance''.
\item Error: In dataabstraction.py: comments for the function
  ``get\_binstances\_satisfying\_state''. Instead of ``Returns a
  BehaviorInstanceList of instances'', should be ``Returns a
  BehaviorInstance(EventGroup) of instances''
\item Observation: To specify dependent fields in a state proposition, the field
  should have been mentioned by the state on which the current state is
  dependent. For example, ``event\_1 = {ip = \$1} event\_2 = {ip =
    event\_1.ip}'' is acceptable. But in ``event\_1 = {uuid = \$1} event\_2 = {ip =
    event\_1.ip}'', ``event\_2'' will be recognized as an independent state.
\item Question: Why is it that when looking for satisfying instances against a
  specific behavior, \saf{} will produce several sub-behaviors which is copy of
  the main behavior? For example, when processing NOVABOOTCOPY, \saf{} produces
  a number of copies: USERMODELS.NOVABOOTCOPY.p381526;
  USERMODELS.NOVABOOTCOPY.b;
  USERMODELS.QUALIFIER;USERMODELS.NOVABOOTCOPY.p551410;
  USERMODELS.NOVABOOTCOPY.p536560; USERMODELS.NOVABOOTCOPY.p989555?
